Accesible, realistic genome simulation with selection using \stdpopsim

### 2025-01-10 analysis2_manuscript.tex
Update analysis2_manuscript.tex
small change to make this build (#43)

\title{Adding selection to \stdpopsim: oh how the tables have turned}
    \kelcomment{Normally, I like quirky, witty titles, but I'm not sure I get this one...what is "how the tables have turned" in reference to? }

@@

\author[5]{Scott T. Small}
% \author[26]{Per Unneberg}
% \author[27]{Juan Manuel Vazquez}
% \author[28]{Ryan K. Waples}
% \author[29]{Anthony Wilder Wohns}
% \author[30]{Yan Wong}
% \author[31]{Franz Baumdicker}
% \author[32]{Reed A. Cartwright}
% \author[33]{Gregor Gorjanc}
\author[4]{Kirk E. Lohmueller}
\author[34]{Ryan N. Gutenkunst}
\author[30]{Jerome Kelleher}
\author[35]{Aaron P. Ragsdale}

@@

    In Figures \ref{fig:vaquita-dfe.constant} and \ref{fig:vaquita-dfe} we show a comparison of estimates
    from the same three DFE-inference packages on simulations of the
    vaquita porpoise genome. Importantly, these simulations use the vaquita demogrpahic model shown in Fig. X and a DFE that includes recessive deleterious mutations, as suggested in Robinsion et al. (2022). All methods
    perform uniformly worse that in the human genome simulations, with consistent underestimation of the mean selection coefficient    
    and overestimation of the shape parameter. This is not surprising as a mis-specified model is being fit to the data. All DFE inference methods used here assume an addive model (no dominance, $h = 1/2$) while the simulated data from the vaquita  was generated from a DFE in which more deleterious mutations are more recessive ($h < 1/2$)

>>>>

\title{Accesible, realistic genome simulation with selection using \stdpopsim}

@@

\author[5]{Scott T. Small}
\author[5]{Clara T. Rehmann}
% \author[26]{Per Unneberg}
% \author[27]{Juan Manuel Vazquez}
% \author[28]{Ryan K. Waples}
% \author[29]{Anthony Wilder Wohns}
% \author[30]{Yan Wong}
% \author[31]{Franz Baumdicker}
% \author[32]{Reed A. Cartwright}
% \author[33]{Gregor Gorjanc}
\author[4]{Kirk E. Lohmueller}
\author[34]{Ryan N. Gutenkunst}
\author[30]{Jerome Kelleher}
\author[35]{Aaron P. Ragsdale}

@@

    In Figures \ref{fig:vaquita-dfe.constant} and \ref{fig:vaquita-dfe} we show a comparison of estimates
    from the same three DFE-inference packages on simulations of the
    vaquita porpoise genome. Importantly, these simulations use the vaquita demogrpahic model shown in Fig. \ref{fig:1pop-vaquita-demography} and a DFE that includes recessive deleterious mutations, as suggested in \cite{robinson2022critically}. All methods
    perform uniformly worse that in the human genome simulations, with consistent underestimation of the mean selection coefficient    
    and overestimation of the shape parameter. This is not surprising as a mis-specified model is being fit to the data. All DFE inference methods used here assume an addive model (no dominance, $h = 1/2$) while the simulated data from the vaquita  was generated from a DFE in which more deleterious mutations are more recessive ($h < 1/2$)
